Staged Abstract Interpreters

### 2019-08-15 paper/50_stageabs.tex
Titles and spaces

\subsection{A Little Bit Code Generation, Again}
The code generation for compiled closures and function applications are similar
to the staged concrete interpreter. We have two the IR node as case classes, they
take additional caches as arguments. We also elide how to generate next-stage Scala
code for them.

>>>>

\subsection{A Little Bit of Code Generation, Again}
The code generation for compiled closures and function applications are similar
to the staged concrete interpreter. We have two the IR node as case classes, they
take additional caches as arguments. We also elide how to generate next-stage Scala
code for them.
